---
title: "CSDE 502 Assignment 4"
author: "[Lizzy Pelletier](mailto:epell@uw.edu)"
date: '`r format(Sys.time(), "%Y-%m-%d %H:%M")`' 
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
output: 
    bookdown::html_document2:
        number_sections: true
        self_contained: true
        code_folding: hide
        toc: true
        toc_float:
            collapsed: true
            smooth_scroll: false
    pdf_document:
        number_sections: true
        toc: true
        fig_cap: yes
        keep_tex: yes
urlcolor: blue        
---

<!--these following settings control width and also make a DIV tag for black outlines for figures-->
<style type="text/css">
.main-container {
  max-width: 2400px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
.outline {
   background-color: #000000;
   padding:1px;
   display: inline-block;
}
</style>


```{r setup, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
# key setups
library(sqldf) # to use sql syntax with data frames
library(knitr) # knitr for kable tables
library(kableExtra) # pretty tables
library(sf) # simple features (GIS)
library(leaflet) # nice maps
library(tools) # md5sum
library(tidyverse)
library(haven)
library(RColorBrewer)
library(bookdown)
# captions
library(captioner)
devtools::install_github("ciannabp/inauguration")
library(inauguration)

table_nums <- captioner(prefix = "Table")
figure_nums <- captioner(prefix = "Figure")



knitr::opts_chunk$set(warning = FALSE, message = FALSE)
cols <- inauguration(name="inauguration_2021")
```

<!-- for a wide presentation -->
<style type="text/css">
.main-container {
  max-width: 2400px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

<!-- a DIV for black outline, good for figures-->
<style>
.outline {
   background-color: #000000;
   padding:1px;
   display: inline-block;
}
</style>

```{r createdata}
gradpain <- c(rep(0,11), rep(1,1), rep(2,2), rep(3,6), rep(4,8), rep(5,10),
rep(6,8), rep(7,30), rep(8,10), rep(9,6), rep(10,2))
```

# Question 1

There are `r length(gradpain)` graduate students in the sample. 

# Question 2

The sample mean is `r mean(gradpain)`.

# Question 3

```{r box1}
# Generate function
sampWithRep <- function(d.vec, n) {
  samp <- sample(d.vec, size=n, replace=TRUE)
  sampsize <- length(samp)
  mean <- mean(samp)
  return(list(sampsize, mean))
}
# Run 100 times with gradpain 
set.seed(7)
means.list <- c()
for (i in 1:100) {
  means.list <- append(means.list, unlist(sampWithRep(gradpain, length(gradpain))[2])) 
}
```

The mean of these 100 means is `r round(mean(means.list),2)`.

# Question 4

The standard deviation of these 100 means is `r round(sd(means.list), 2)`. 

# Question 5

```{r box3}
sampWithRepNTimes <- function(d.vec, n, num.samples) {
  means.list <- c()
  for (i in 1:num.samples) {
      means.list <- append(means.list, mean(sample(d.vec, size=n, replace=TRUE)))
  }
  mn <- mean(means.list)
  sd <- sd(means.list)
  confint <- c(mn - (1.96*sd), mn + (1.96*sd))
  return(
    list(
      n,
      num.samples,
      means.list,
      mn,
      sd,
      confint
    )
  )
}

# run the function
res <- sampWithRepNTimes(d.vec=gradpain, n=length(gradpain), num.samples=100)

```

The function returns `r round(unlist(res[4]), 2)` as the mean of means.

# Question 6

The function returns `r round(unlist(res[5]), 2)` as the standard deviation of the means.

# Question 7

The function returns [`r round(unlist(res[6]), 2)`] as the 95% confidence interval around the mean.

# Source code

## This document
```{r comment=''}
cat(readLines("~/Dropbox/Classes/Q2/CSDE 502/Week04/week_04.Rmd"), sep = '\n')
```
